Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-03-21 paper.tex
Add Matt's responses to TODO notes

In fact a spherical steady-state wind model, though providing an adequate
backdrop for the qualitative study presented in this section,
is less than ideal for this post-merger configuration,
most obviously because in the 10~ms since merger,
ejecta with the greatest velocities around $0.3c$
will have reached no further than $r_{\rm max} \sim 10^8$~cm.
Additionally, the true radial profile of the ejecta from this merger
(which our computational model does not follow)
will have many more features inside this radius, including shock jumps.
This model density profile is adequate as a backdrop to our study here, however,
since we expect the remnant to present similar neutrino emission over a thermal
timescale of a few tens of milliseconds
\footnote{TODO (Matt, Francois): reasonable assumption? citation?}
while the matter field propagates out to larger radii.

>>>>

In fact a spherical steady-state wind model, though providing an adequate
backdrop for the qualitative study presented in this section,
is less than ideal for this post-merger configuration,
most obviously because in the 10~ms since merger,
ejecta with the greatest velocities around $0.3c$
will have reached no further than $r_{\rm max} \sim 10^8$~cm.
Additionally, the true radial profile of the ejecta from this merger
(which our computational model does not follow)
will have many more features inside this radius, including shock jumps.
This model density profile is adequate as a backdrop to our study here, however,
since we expect the remnant to present similar neutrino emission over a thermal
timescale of a few tens of milliseconds
while the matter field propagates out to larger radii.
